agdarsec -- Total Parser Combinators

### 2017-10-31 doc/paper/main.tex
[ fix ] forgot to mention Char -> Tok

Similarly, there is no reason to force the user to get back a \emph{list}
of successes: any alternative monad will do. This means in particular that
a user may for instance instrument a parser with a logging ability to be
able to return good error messages, have a (re)configurable grammar using
a \type{Reader} transformer or use a \type{Maybe} type if they want to make
explicit the fact that their grammar is unambiguous.

>>>>

Secondly, there is no reason to limit ourselves to \type{Char} as the
unit of information to be processed. Near all of our combinators are
fully polymorphic over the kind of tokens they can deal with. To run
the parser, the user will have to declare an instance of the \AR{Tokenizer}
class corresponding to their use case. The library provides a trivial
one for \AD{Char}.

Thirdly, there is no reason to force the user to get back a \emph{list}
of successes: any alternative monad will do. This means in particular that
a user may for instance instrument a parser with a logging ability to be
able to return good error messages, have a (re)configurable grammar using
a \type{Reader} transformer or use a \type{Maybe} type if they want to make
explicit the fact that their grammar is unambiguous.
